### 2014-01-14 arfi_methods.tex
updated text formatting

3D volumetric imaging data was acquired using mechanical rotation of the ER7B
transducer between sequential imaging frames, sweeping across the lateral
extent of the prostate.  This rotation setup utilized a CIVCO
Micro-Touch\texttrademark stabalizer (CIVCO Medical Solutions, Kalona, IA USA)
that allows for complete 6-axis degrees of freedom for manual positioning of
the transducer to sweep through the entire prostate during imaging.  Sequential
imaging frames were $\sim$ 1-2\degree apart, depending on the absolute size of the
prostate.  A custom optical angular feedback transduction circuit utilizing a
reflective linear strip with 500 lines-per-inch (LPI) resolution (US Digital,
Vancouver, WA, USA) was coupled with a 141 oz-in torque stepper motor with
planetary gearbox (Model \#11YPG202S-LW4-R27, Anaheim Automation, Anaheim, CA,
USA) (Figure~\ref{fig:setup_annotated}) to achieve accurate spatial
localization of the imaging frames in the 3D dataset.

@@

>>>>

3D volumetric imaging data was acquired using mechanical rotation of the ER7B
transducer between sequential imaging frames, sweeping across the lateral
extent of the prostate.  This rotation setup utilized a CIVCO
Micro-Touch\texttrademark stabalizer (CIVCO Medical Solutions, Kalona, IA USA)
that allows for complete 6-axis degrees of freedom for manual positioning of
the transducer to sweep through the entire prostate during imaging.  Sequential
imaging frames were $\sim$1\degree apart, depending on the absolute size of the
prostate.  A custom optical angular feedback transduction circuit utilizing a
reflective linear strip with 500 lines-per-inch (LPI) resolution (US Digital,
Vancouver, WA, USA) was coupled with a 141 oz-in torque stepper motor with
planetary gearbox (Model \#11YPG202S-LW4-R27, Anaheim Automation, Anaheim, CA,
USA) (Figure~\ref{fig:setup_annotated}) to achieve accurate spatial
localization of the imaging frames in the 3D dataset.

@@

The normalized displacement data were scan-converted using a Delaunay
triangulation method with XXXX commaind in Matlab (R2012b, XXXX).  The
scan-converted ARFI imaging data had a final voxel size of XX x XX x XX mm.

### 2014-01-14 fig_setup_annotated.tex
updated text formatting

\begin{figure}[htb!]
\centering
\includegraphics[width=0.75\textwidth]{figs/setup_annotated.png}
\caption{The experimental setup used for ARFI imaging in the operating suite,
    including the Siemens SC2000 scanner with the ER7B endorectal transducer
    sitting in a custom cradle of a CIVCO Micro-Touch\texttrademark stabalizer
    with optical feedback controlling a stepper motor to acquire 3D ultrasound
    imaging data \invivo.  Custom-written Python code was run on the scanner to
    trigger B-mode and ARFI imaging acquisition sequences relative to completed
    rotation increments of $\sim$ 1-2\degree.}
\label{fig:setup_annotated} 
\end{figure}

>>>>

\begin{figure}[htb!]
\centering
\includegraphics[width=0.75\textwidth]{figs/setup_annotated.png}
\caption{The experimental setup used for ARFI imaging in the operating suite,
    including the Siemens SC2000 scanner with the ER7B endorectal transducer
    sitting in a custom cradle of a CIVCO Micro-Touch\texttrademark stabalizer
    with optical feedback controlling a stepper motor to acquire 3D ultrasound
    imaging data \invivo.  Custom-written Python code was run on the scanner to
    trigger B-mode and ARFI imaging acquisition sequences relative to completed
    rotation increments of $\sim$1\degree.}
\label{fig:setup_annotated} 
\end{figure}
